---
title: "MasterWrapper"
author: "Anna Stuckert"
date: "9/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Evt indsæt en settings blok med fx farvekoder

#Preparation
```{r}
#Read in packages
pacman::p_load(here, tidyverse, dplyr)


#Get data
source(here("data", "read_raw_data.r"))


#Run data preprocessing script
source(here::here("code", "get_scores_function_finished_nodropna.R"))
scores = get_scores(data)


source(here::here("code", "get_clean_data.R"))
clean_data = get_clean_data(data)


#source(here::here("code", "combine_intero_survey_BE_data.R"))
#data_survey_BE_intero <- combine_intero_survey_BE_data(scores)




#Manual in-script preprocessing

Intero_data <- read_delim(here::here("Data", 'Behavior.txt'),  delim=",")

#Clean values in subject column for sub_0XXX
Intero_data$Subject <- gsub("sub_0+", "", Intero_data$Subject) %>% as.integer()
Intero_data <- Intero_data %>% rename(record_id= Subject)

#OBS intero data in long format, so 2 rows for each subject, one of rintero condition, one for extero
#just converting extero to NAs and dropping NAs for now (possibly also dropping other NAs)


# Intero_data$Modality <- ifelse(Intero_data$Modality == "Intero", "Intero", NA)
# Intero_data <- Intero_data %>% drop_na()

#Merge survey + interoception data
data <- merge(scores, Intero_data, by.y = "record_id")

#Load brain explorer data
BE_treasure=read.csv(here::here("Data", 'Cobelab_TreasureHunt.csv'))
BE_scavenger=read.csv(here::here("Data", 'Cobelab_Scavenger.csv'))

#renaming ID columns
BE_treasure <- BE_treasure %>% rename(be_id= user_ID)
BE_scavenger <- BE_scavenger %>% rename(be_id= user)

#Adding column for mean gambling attitude win/loss
BE_scavenger <- BE_scavenger %>% mutate(perc_risk_abg= rowMeans(.[, 5:6]))
BE_scavenger <- BE_scavenger %>% mutate(perc_risk_NoAbg= rowMeans(.[, 7:8]))

#merging with survey+interoception data
#data <- merge(data, BE_treasure, by.y = "be_id")
#data <- merge(data, BE_scavenger, by.y = "be_id")


```

scatterplot matrix for accuracy, dprime, criterion, threshold and slope
```{r}

### Correlation heatmap comparing modalities

# Intero_data$Modality <- ifelse(Intero_data$Modality == "Intero", "Intero", NA)
# Intero_data <- Intero_data %>% drop_na()
intero_df <- Intero_data
intero_df$Modality <- ifelse(intero_df$Modality == "Intero", "Intero", NA)
intero_df <- intero_df %>% drop_na()

extero_df <- Intero_data
extero_df$Modality <- ifelse(extero_df$Modality == "Extero", "Extero", NA)
extero_df <- extero_df %>% drop_na()

extero_df <- extero_df %>% 
    rename(
      Ex_Accuracy = Accuracy,
      Ex_threshold = Threshold,
      Ex_Criterion = Criterion,
      Ex_Slope = Slope,
      Ex_dPrime = dPrime
    )

intero_df <- intero_df %>% 
    rename(
      In_Accuracy = Accuracy,
      In_threshold = Threshold,
      In_Criterion = Criterion,
      In_Slope = Slope,
      In_dPrime = dPrime
    )

combined_ex_in_df <- cbind(extero_df, intero_df)


#data$Modality <- ifelse(data$Modality == "Intero", "Intero", NA)
#data <- data %>% drop_na()

combined_shortened <- select(combined_ex_in_df, matches("In_|Ex_"))

pairs(combined_shortened, pch = 19)


#Correlation plot

  cormat <- round(cor(combined_shortened),2)
  
  head(cormat)
  
  #fixing matrix
  cormat<- cormat[,-6:-10]
  cormat<- cormat[-1:-5,]
  
  
  library(reshape2)
  melted_cormat <- melt(cormat)
  head(melted_cormat)
  
  plot_out <- ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
    geom_tile()+
    ylab("Variables")+ 
    xlab("Variables")+
    ggtitle("Correlation matrix for interoception variables")+
    scale_fill_viridis_c(option = "inferno")+
    labs(fill= "Pearson correlation coefficient")

plot_out





### correlation heatmap within one modality

#int_shortened <- select(data, "Threshold", "Criterion", "Slope", "dPrime", "Accuracy","perc_risk_NoAbg", "perc_optimal_all", "perc_loss_risk_NoAbg","PSS")

pairs(int_shortened, pch = 19)


#Correlation plot

  cormat <- round(cor(int_shortened),2)
  
  head(cormat)
  
  #fixing matrix
  # cormat<- cormat[,-13:-16]
  # cormat<- cormat[-1:-12,]
  
  
  library(reshape2)
  melted_cormat <- melt(cormat)
  head(melted_cormat)
  
  plot_out <- ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
    geom_tile()+
    ylab("Exteroception variable")+ 
    xlab("Interoception variables")+
    ggtitle("Correlation matrix for interoception variables")+
    scale_fill_viridis_c(option = "inferno")+
    labs(fill= "Pearson correlation coefficient")

plot_out


```

# Interoception data exploration

Correlation plot (non-corrected for multiple comparisons)

```{r}
str(Intero_data)
int_data <- as.matrix(Intero_data)

int_data <- select(Intero_data, -matches("X1|record_id|Modality"))

  cormat <- round(cor(int_data),2)
  head(cormat)
  
  #fixing matrix
  # cormat<- cormat[,-13:-16]
  # cormat<- cormat[-1:-12,]
  
  
  library(reshape2)
  melted_cormat <- melt(cormat)
  head(melted_cormat)
  
  plot_out <- ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
    geom_tile()+
    ylab("Variables")+ 
    xlab("Variables")+
    ggtitle("Correlation matrix for interoception variables")+
    scale_fill_viridis_c(option = "inferno")+
    labs(fill= "Pearson correlation coefficient")

plot_out
```

Correlelogram corrected for multiple comparisons

```{r}
# for reproducibility
set.seed(123)

install.packages("ggstatsplot")
library(ggstatsplot)

# as a default this function outputs a correlation matrix plot
ggstatsplot::ggcorrmat(
  data = int_data,
  type = "robust", # correlation method
  p.adjust.method = "holm", # p-value adjustment method for multiple comparisons
  cor.vars = c("Accuracy", "Confidence", "ConfidenceRT", "Criterion", "EstimationRT", "HBC", "Slope", "TaskDuration", "Threshold","dPrime"), # a range of variables can be selected
  cor.vars.names = c("Accuracy", "Confidence", "ConfidenceRT", "Criterion", "EstimationRT", "HBC", "Slope", "TaskDuration", "Threshold","dPrime"),
  matrix.type = "upper", # type of visualization matrix
  colors = c("#B2182B", "white", "#4D4D4D"),
  title = "Correlalogram for Interoception data",
  caption = "Source: `ggplot2` R package"
)


#GROUPED

# for reproducibility
set.seed(123)


int_data <- select(Intero_data, -matches("X1|record_id"))

# plot
ggstatsplot::grouped_ggcorrmat(
  data = int_data,
  cor.vars = c("Accuracy", "Confidence", "ConfidenceRT", "Criterion", "EstimationRT", "HBC", "Slope", "TaskDuration", "Threshold","dPrime"), # a range of variables can be selected
  colors = c("#cbac43", "white", "#550000"),
  grouping.var = Modality, # grouping variable
  k = 2L, # number of digits after decimal point
  title.prefix = "Interoception",
  p.adjust.method= "bonferroni",
  insig = "blank"
)

#If adjusted p-values are displayed in the visualization of correlation matrix, the adjusted p-values will be used for the upper triangle, while unadjusted p-values will be used for the lower triangle of the matrix.

# For intero vs extero variables
# plot
ggstatsplot::grouped_ggcorrmat(
  data = int_data,
  cor.vars = c("Accuracy", "Confidence", "ConfidenceRT", "Criterion", "EstimationRT", "HBC", "Slope", "TaskDuration", "Threshold","dPrime"), # a range of variables can be selected
  colors = c("#cbac43", "white", "#550000"),
  grouping.var = Modality, # grouping variable
  k = 2L, # number of digits after decimal point
  title.prefix = "Interoception",
  p.adjust.method= "bonferroni",
  insig = "blank"
)

```

Simple modelling of interoception
```{r}

m1<- lm(Confidence~ Accuracy + Slope + Threshold, data= int_data)
summary(m1)
```



#N DRAWS
```{r}
## ADHD plots with n_draw
#ADHD combined a and b
ggplot(data, aes(asras_ab_combined, n_draws))+
  geom_point()+
  geom_smooth(method="lm")

#ADHD a
ggplot(data, aes(asra_a, n_draws))+
  geom_point()+
  geom_smooth(method="lm")

#ADHD b
ggplot(data, aes(asrs_b, n_draws))+
  geom_point()+
  geom_smooth(method="lm")
```

```{r}
# OCD plots

ggplot(data, aes(oci_r, n_draws))+
  geom_point()+
  geom_smooth(method="lm")
```

```{r}
cor.test(data$asras_ab_combined, data$n_draws, method=c("spearman"))
cor(data$asras_ab_combined, data$n_draws, method=c("spearman"))

cor.test(data$asra_a, data$n_draws, method=c("spearman"))
cor.test(data$asrs_b, data$n_draws, method=c("spearman"))

cor.test(data$oci_r, data$n_draws, method=c("spearman"))
cor(data$oci_r, data$n_draws, method=c("spearman"))
```

#GAMBLING

```{r}
# win abg vs NoAbg

ggplot(BE_scavenger, aes(perc_win_risk_abg, perc_win_risk_NoAbg))+
  geom_point()+
  geom_smooth(method="lm")

# Loss abg vs NoAbg
ggplot(BE_scavenger, aes(perc_loss_risk_abg, perc_loss_risk_NoAbg))+
  geom_point()+
  geom_smooth(method="lm")

#mean gambling score abg vs NoAbg
# Loss abg vs NoAbg
ggplot(BE_scavenger, aes(perc_risk_abg, perc_risk_NoAbg))+
  geom_point()+
  geom_smooth(method="lm")
```

#correlation tests
```{r}
cor.test(BE_scavenger$perc_win_risk_abg, BE_scavenger$perc_win_risk_NoAbg, method=c("spearman"))
cor.test(BE_scavenger$perc_loss_risk_abg, BE_scavenger$perc_loss_risk_NoAbg, method=c("spearman"))

#combined 
cor.test(BE_scavenger$perc_loss_risk_abg, BE_scavenger$perc_risk_NoAbg, method=c("spearman"))
```

#Modelling
```{r}
lm(perc_risk_NoAbg~perc_loss_risk_abg, BE_scavenger)

```


#PLOTTING 
"interoception and risk aversion
```{r}
#mean gambling score abg vs NoAbg
# Loss abg vs NoAbg
ggplot(data, aes(dPrime, perc_loss_risk_NoAbg))+
  geom_point()+
  geom_smooth(method="lm")

#combined 
cor.test(data$Threshold, data$perc_optimal_all, method=c("spearman"))
```

