---
title: "MasterWrapper"
author: "Anna Stuckert"
date: "9/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Evt indsæt en settings blok med fx farvekoder

#Preparation
```{r}
#Read in packages
pacman::p_load(here, tidyverse, dplyr, corrplot, reshape2, ggthemes, ggsci)

#Get survey-data with demographics and IDs
source(here("data", "read_psychometrics_data.r"))

#Run data preprocessing script
source(here::here("code", "get_scores_function.R"))
scores = get_scores(data)
data <- scores

# Removing 44 and 46, becuase they have pseudo ID's and 1108 as this is Nanna testing if redcap surveys work
data <- filter(data, record_id != 44 & record_id != 46 &  record_id != 1108 &  record_id != 222)


#Inserting new, true Observations under their correct ID numbers
#  5934 = 44
data$record_id <- ifelse(data$record_id == 5934, 44, data$record_id)

#  5992 = 46
data$record_id <- ifelse(data$record_id == 5992, 46, data$record_id)

# 6335 = 222
data$record_id <- ifelse(data$record_id == 6335, 222, data$record_id)

#Get interoception task data
Intero_data <- read_delim(here::here("Data", 'Behavior.txt'),  delim=",")

#Clean values in subject column for sub_0XXX
Intero_data$Subject <- gsub("sub_0+", "", Intero_data$Subject) %>% as.integer()
Intero_data <- Intero_data %>% rename(record_id= Subject)

#create column for absolute value of Threshold (as a value of 0 indicates precise interoception, while anything above and below indicates bias)
Intero_data <- Intero_data %>% mutate(absolute_threshold = abs(Threshold))

#drop data that is not from del 1
Intero_data$Session <- ifelse(Intero_data$Session == "Del1", "Del1", NA)
Intero_data<- Intero_data[!is.na(Intero_data$Session),]

#Merge survey + interoception data
#data <- merge(data, Intero_data, by.y = "record_id")

#Load brain explorer Scavenger task data
BE_scavenger=read.csv(here::here("Data", 'Cobelab_Scavenger.csv'))

#renaming ID columns
BE_scavenger <- BE_scavenger %>% rename(be_id= user)

#Adding column for mean gambling attitude ambigious/non-ambigous
BE_scavenger <- BE_scavenger %>% mutate(perc_risk_abg= rowMeans(.[, 5:6]))
BE_scavenger <- BE_scavenger %>% mutate(perc_risk_NoAbg= rowMeans(.[, 7:8]))

#I considered that maybe a proxy for loss aversion could be to subtract perc_loss_risk from perc_win_risk (perc_loss_risk - perc_win_risk) so people people with positive values would reflect that people were more likely to choose risk when faces with a loss than for a win (which could maybe be interpreted that they would by all means try to avoid a loss at all)
BE_scavenger <- BE_scavenger %>% mutate(proxy_loss_aversion = perc_loss_risk - perc_win_risk)

# Create column for interaction effect between variables
BE_scavenger <- BE_scavenger %>% mutate(Interaction_framing_ambiguity = ((perc_win_risk_abg - perc_loss_risk_abg) - (perc_win_risk_NoAbg - perc_loss_risk_NoAbg)))


#merging with survey+interoception data
data <- merge(data, BE_scavenger, by.y = "be_id")

#removing datapoints from faulty HRD participants
#data <- filter(data, record_id != 54 & record_id != 84 &  record_id != 192)

#drop extero modality
#int_ex_data <- data
#data$Modality <- ifelse(data$Modality == "Intero", "Intero", NA)
#data<- data[!is.na(data$Modality),]

write_csv(data, "all_data_BE_psychometrics.csv")


```

# Total number of participants
  # 225 have "completed" the questionnaire
  # 216 people have completed the HRD 
  # 197/196 have completed the scavenger task
  # 189 people have completed both the HRD and the scavenger 

# Total number excluded 
  # 0033  Don't have HRD data 
  # 0036  Don't have questionaire data as they were excluded from the experiment (+ invalid responses -> remove)
  # 0041  Don't have questionaire data as they were excluded from the experiment
  # 0043  We don't have brain explorer id from them 
  # 0110  Don't have questionaire data+ we don't have brain ID data from them
  # 0192  Are still in the data set, have both HRD and questionaire - marked with grey in
  log sheet, neurologial disorder
  # Subject 44, 45, 46: data missing
  # Subject 54: noisy PPG -> remove
  # Subject 141: no data (crash?)
  
  
  Subjects unanswered:
  191
  210
  223
  248
  249
  
  HBC - question: should we remove these data, if we don't use HBC in our analyses?
  # Subject 21, 31, 44, 45, 49, 50, 62: missing data?
  # Subject 25, 41: incomplete (crash?)
  
  to do:
DELETE 192!!!
Subject 54: noisy PPG -> remove
Subject 84: bad confidence ratings -> remove

  #from nicolas
  HRD - questions:
Subject 46: you said data was missing, but the HRD data is there - 44 and 45 is missing. 
Subject 27: rename file (28->27) - But in the intero data we both have, there are BOTH a subject 27 and 28. It doesn't seem to rename , wouldnøt we override some data that way?
Subject 74: missing data - No it's there???
Subject 81: incorrect file name (081) - but the data is there?? we have just removed the first 0 in 081.

HRD to do (aka to remove)
Subject 54: noisy PPG -> remove
Subject 84: bad confidence ratings -> remove

HBC - question: should we remove these data, if we don't use HBC in our analyses?
Subject 21, 31, 44, 45, 49, 50, 62: missing data?
Subject 25, 41: incomplete (crash?)

DEMOGRAPHICS
```{r}
# Mean task duration of HRD
mean(data$TaskDuration) # mean task duration is 31.5 min. 
sd(data$TaskDuration) #sd = 3.9 min

# mean age 
mean(data$age) # mean age is 24.89
sd(data$age) # sd of 5.04

# Gender distribtuion
# Number of men, women, other
gender <- data %>%
  group_by(gender)%>%
  summarise(count = n())
            # 1 = Woman = 111
            # 2 = men = 74
            # 3 = other = 1 

```

SANITY CHECK PLOTS HRD

```{r}

### PLOTS FOR USE ###

#Currently using data only from participants included for all analyses (i.e. having completed both Scavenger task and HRD - the sanity checks for HRD should possibly be run with all participants having complete HRD, but then the int_ex_data data can be switched with Intero_dat)


#OBS if we want to use red/blue combination (to make it work with Nicolas' plots) - use Set1 from the brewer color schemes, and use "dark red" and "dark blue" for density distributions.

# Plot of slope 
SL <- ggplot(data= int_ex_data, aes(x= Modality, y= Slope, color = Modality, fill = Modality )) +
  geom_bar(stat="summary", fun.y = mean)+
  theme_stata(scheme = "s1color")+
  scale_color_brewer(palette = "Paired")+
  scale_fill_brewer(palette = "Paired")+
  geom_errorbar(stat="summary", fun.data=mean_se, color = "black", width = 0.7)

SL


# mean slope per modality 
Slope_pr_modality <- int_ex_data %>%
  group_by(Modality)%>%
  summarise(mean(Slope))  
   # Extero =  13.23782
    # Intero = 15.53700



slope_violin <- ggplot(int_ex_data, aes(x= Modality, y= Slope, color = Modality)) + 
  scale_color_brewer(palette = "Paired")+
  scale_fill_brewer(palette = "Paired")+
  theme_stata(scheme = "s1color")+ 
  geom_violin()+ 
  geom_boxplot(width=0.1)

slope_violin

# large slope = uncertain decision 
# This plot shows that participants are less certain/precise about the stimuli being faster or slower than their own heart beat for the intero condition than for the extero condition

# Plot of threshold 
thres_violin <- ggplot(int_ex_data, aes(x= Modality, y= Threshold, color = Modality)) + 
  geom_violin()+ 
  geom_boxplot(width=0.1)+
  theme_stata(scheme = "s1color")+ 
  scale_color_brewer(palette = "Paired")

thres_violin
# Participants are biased in the intero condition. Generally think their heart rate is slower than it actually is. They need more information to become better. 
  

# mean threshold per modality 
Thres_pr_modality<- int_ex_data %>%
  group_by(Modality)%>%
  summarise(mean(Threshold))  
    # extero = 1.035241	
    # Intero = -7.684271	


# Participants are more accurate for extero conditions compared to intero conditions 


# Confidence is invertly related to slope.
# Nu større slope er nu mindre præcise er deltagerne i at høre/mærke forksllen på om det er hurtigere eller langsommere end deres hjerne. # Nu mere upræcise de er nu mere usikre er de. 

acc_RT <- ggplot(data= int_ex_data, aes(x= DecisionRT, y= Accuracy, color = Modality)) +
  geom_point()+
  geom_smooth(method = lm)+
  theme_stata(scheme = "s1color")+
  scale_color_brewer(palette = "Paired")+
  xlab("Mean reaction time per participant")+
  ylab("Mean accuracy per participant")

acc_RT

# COMBINED DENSITY PLOTS

dens_acc <- ggplot(data = int_ex_data, aes (Accuracy, color = Modality))+
  geom_density( alpha = 0.5)+
  theme_stata(scheme = "s1color")+
  scale_color_brewer(palette = "Paired")+
  xlab("Accuracy")

dens_acc

dens_thres <- ggplot(data = int_ex_data, aes (Threshold, color = Modality))+
  geom_density(alpha = 0.5)+
  theme_stata(scheme = "s1color")+
  scale_color_brewer(palette = "Paired")+
  xlab("Threshold")

dens_thres

dens_slope <- ggplot(data = int_ex_data, aes (Slope, color = Modality))+
  geom_density(alpha = 0.5)+
  theme_stata(scheme = "s1color")+
  scale_color_brewer(palette = "Paired")+
  xlab("Slope")

dens_slope

library(cowplot)
plot_row<- plot_grid(dens_acc, dens_thres, dens_slope)
plot_row

#HBC plot, showing that thres correlates with HBC = shows more or less that both tasks work.
# HBC <- ggplot(data= int_ex_data, aes(x= Threshold, y = HBC, color = Modality)) +
#   geom_point()+
#   geom_smooth(method = lm)+
#   theme_stata(scheme = "s1color")+
#   scale_colour_stata("s2color")
# 
# HBC

# Checking for celing effects in distributions of interoception variables for each modality

# Creating new data frame
intero_df <- int_ex_data

# Only putting intero into this data frame 
intero_df$Modality <- ifelse(intero_df$Modality == "Intero", "Intero", NA)
# Removing NA 
intero_df <- intero_df[!is.na(intero_df$Modality),]

# Creating new datafram 
extero_df <- int_ex_data

# Only putting extreo into this dataframe 
extero_df$Modality <- ifelse(extero_df$Modality == "Extero", "Extero", NA)
# Removing NA 
extero_df <-  extero_df[!is.na(extero_df$Modality),]

extero_df <- extero_df %>% 
    rename(
      Ex_Accuracy = Accuracy,
      Ex_Threshold = Threshold,
      Ex_Criterion = Criterion,
      Ex_Slope = Slope,
      Ex_dPrime = dPrime
    )

intero_df <- intero_df %>% 
    rename(
      In_Accuracy = Accuracy,
      In_Threshold = Threshold,
      In_Criterion = Criterion,
      In_Slope = Slope,
      In_dPrime = dPrime
    )

dens_acc_In <- ggplot(data = intero_df, aes (In_Accuracy))+
  geom_density(color = "darkblue", fill = "darkblue", alpha = 0.5)+
  theme_stata(scheme = "s1color")+
  xlab("Slope for interoception")

dens_acc_In

dens_acc_Ex <- ggplot(data = extero_df, aes (Ex_Accuracy))+
  geom_density(color = "lightblue", fill = "lightblue", alpha = 0.5)+
  theme_stata(scheme = "s1color")+
  xlab("Slope for interoception")

dens_acc_Ex

# The density plots revaled no celling effect 

dens_slope_In <- ggplot(data = intero_df, aes (In_Slope))+
  geom_density(color = "darkblue", fill = "darkblue", alpha = 0.5)+
  theme_stata(scheme = "s1color")+
  xlab("Slope for interoception")

dens_slope_In

dens_slope_Ex <- ggplot(data = extero_df, aes (Ex_Slope))+
  geom_density(color = "lightblue", fill = "lightblue", alpha = 0.5)+
  theme_stata(scheme = "s1color")+
  xlab("Slope for interoception")

dens_slope_Ex

#The density plot for interoception revealed a ceiling effect, but it's not too bad.

dens_thres_In <- ggplot(data = intero_df, aes (In_Threshold))+
  geom_density(color = "darkblue", fill = "darkblue", alpha = 0.5)+
  theme_stata(scheme = "s1color")+
  xlab("Slope for interoception")

dens_thres_In

dens_thres_Ex <- ggplot(data = extero_df, aes (Ex_Threshold))+
  geom_density(color = "lightblue", fill = "lightblue", alpha = 0.5)+
  theme_stata(scheme = "s1color")+
  xlab("Slope for interoception")

dens_thres_Ex

# The density plots revaled no celling effect 

# SLOPE AND CONFIDENCE ARE CORRELATED
#bias in extero conditon dos not predict bias in intero condition. 
# In extero you don't have an overall bias to think your heart is slower. This is a very nice finding, shows that it is better than other tasks. 

```






```{r}


df1 <- Intero_data
df2 <- scores

df1 <- select(df1, record_id)
df2 <- select(df2, record_id)

df1 <- rename(df1, intero_id = record_id)
df2 <- rename(df2, survey_id = record_id)

df3 <- combine.df(df1, df2)

for (i in df3$survey_id) {
  df3$match_surv <- ifelse(match(df3$survey_id, df3$intero_id), 0, df3$survey_id)
  df3$excess_survey_id <- ifelse(is.na(df3$match_surv), df3$survey_id, NA)
  return(df3)
}
sum(!is.na(df3$excess_survey_id))

#where excess_survey_id are the stormDB IDs present in the survey data that are NOT present in the intero data.

for (i in df3$intero_id) {
  df3$match_intero <- ifelse(match(df3$intero_id, df3$survey_id), 0, df3$intero_id)
  df3$excess_intero_id <- ifelse(is.na(df3$match_intero), df3$intero_id, NA)
  return(df3)
}

sum(!is.na(df3$excess_intero_id))

df_lack <- df3[!is.na(df3$excess_survey_id),]

```

scatterplot matrix for accuracy, dprime, criterion, threshold and slope
```{r}

### Correlation heatmap comparing modalities

# Intero_data$Modality <- ifelse(Intero_data$Modality == "Intero", "Intero", NA)
# Intero_data <- Intero_data %>% drop_na()
intero_df <- Intero_data
intero_df$Modality <- ifelse(intero_df$Modality == "Intero", "Intero", NA)
intero_df <- intero_df %>% drop_na()

extero_df <- Intero_data
extero_df$Modality <- ifelse(extero_df$Modality == "Extero", "Extero", NA)
extero_df <- extero_df %>% drop_na()

extero_df <- extero_df %>% 
    rename(
      Ex_Accuracy = Accuracy,
      Ex_Threshold = Threshold,
      Ex_Criterion = Criterion,
      Ex_Slope = Slope,
      Ex_dPrime = dPrime
    )

intero_df <- intero_df %>% 
    rename(
      In_Accuracy = Accuracy,
      In_Threshold = Threshold,
      In_Criterion = Criterion,
      In_Slope = Slope,
      In_dPrime = dPrime
    )

combined_ex_in_df <- cbind(extero_df, intero_df)


#data$Modality <- ifelse(data$Modality == "Intero", "Intero", NA)
#data <- data %>% drop_na()

combined_shortened <- select(combined_ex_in_df, matches("In_|Ex_"))
int_shortened <- select(combined_ex_in_df, matches("In_"))

pairs(combined_shortened, pch = 19)


#Correlation plot

  cormat <- round(cor(combined_shortened),2)
  
  head(cormat)
  
  #fixing matrix
  cormat<- cormat[,-6:-10]
  cormat<- cormat[-1:-5,]
  
  
  library(reshape2)
  melted_cormat <- melt(cormat)
  head(melted_cormat)
  
  plot_out <- ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
    geom_tile()+
    ylab("Variables")+ 
    xlab("Variables")+
    ggtitle("Correlation matrix for interoception variables")+
    scale_fill_viridis_c(option = "inferno")+
    labs(fill= "Pearson correlation coefficient")

plot_out





### correlation heatmap within one modality

#int_shortened <- select(data, "Threshold", "Criterion", "Slope", "dPrime", "Accuracy","perc_risk_NoAbg", "perc_optimal_all", "perc_loss_risk_NoAbg","PSS")

pairs(int_shortened, pch = 19)


#Correlation plot

  cormat <- round(cor(int_shortened),2)
  
  head(cormat)
  
  #fixing matrix
  # cormat<- cormat[,-13:-16]
  # cormat<- cormat[-1:-12,]
  
  
  library(reshape2)
  melted_cormat <- melt(cormat)
  head(melted_cormat)
  
  plot_out <- ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
    geom_tile()+
    ylab("Exteroception variable")+ 
    xlab("Interoception variables")+
    ggtitle("Correlation matrix for interoception variables")+
    scale_fill_viridis_c(option = "inferno")+
    labs(fill= "Pearson correlation coefficient")

plot_out


```

# Interoception data exploration

Correlation plot (non-corrected for multiple comparisons)

```{r}
str(Intero_data)
int_data <- as.matrix(Intero_data)

int_data <- select(Intero_data, -matches("X1|record_id|Modality"))

  cormat <- round(cor(int_data),2)
  head(cormat)
  
  #fixing matrix
  # cormat<- cormat[,-13:-16]
  # cormat<- cormat[-1:-12,]
  
  
  library(reshape2)
  melted_cormat <- melt(cormat)
  head(melted_cormat)
  
  plot_out <- ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
    geom_tile()+
    ylab("Variables")+ 
    xlab("Variables")+
    ggtitle("Correlation matrix for interoception variables")+
    scale_fill_viridis_c(option = "inferno")+
    labs(fill= "Pearson correlation coefficient")

plot_out
```

Correlelogram corrected for multiple comparisons

```{r}
# for reproducibility
set.seed(123)

install.packages("ggstatsplot")
library(ggstatsplot)

# as a default this function outputs a correlation matrix plot
ggstatsplot::ggcorrmat(
  data = int_data,
  type = "robust", # correlation method
  p.adjust.method = "holm", # p-value adjustment method for multiple comparisons
  cor.vars = c("Accuracy", "Confidence", "ConfidenceRT", "Criterion", "EstimationRT", "HBC", "Slope", "TaskDuration", "Threshold","dPrime"), # a range of variables can be selected
  cor.vars.names = c("Accuracy", "Confidence", "ConfidenceRT", "Criterion", "EstimationRT", "HBC", "Slope", "TaskDuration", "Threshold","dPrime"),
  matrix.type = "upper", # type of visualization matrix
  colors = c("#B2182B", "white", "#4D4D4D"),
  title = "Correlalogram for Interoception data",
  caption = "Source: `ggplot2` R package"
)


#GROUPED

# for reproducibility
set.seed(123)


int_data <- select(Intero_data, -matches("X1|record_id"))

# plot
ggstatsplot::grouped_ggcorrmat(
  data = int_data,
  cor.vars = c("Accuracy", "Confidence", "ConfidenceRT", "Criterion", "EstimationRT", "HBC", "Slope", "TaskDuration", "Threshold","dPrime"), # a range of variables can be selected
  colors = c("#cbac43", "white", "#550000"),
  grouping.var = Modality, # grouping variable
  k = 2L, # number of digits after decimal point
  title.prefix = "Interoception",
  p.adjust.method= "bonferroni",
  insig = "blank"
)

#If adjusted p-values are displayed in the visualization of correlation matrix, the adjusted p-values will be used for the upper triangle, while unadjusted p-values will be used for the lower triangle of the matrix.

# For intero vs extero variables
# plot
ggstatsplot::grouped_ggcorrmat(
  data = int_data,
  cor.vars = c("Accuracy", "Confidence", "ConfidenceRT", "Criterion", "EstimationRT", "HBC", "Slope", "TaskDuration", "Threshold","dPrime"), # a range of variables can be selected
  colors = c("#cbac43", "white", "#550000"),
  grouping.var = Modality, # grouping variable
  k = 2L, # number of digits after decimal point
  title.prefix = "Interoception",
  p.adjust.method= "bonferroni",
  insig = "blank"
)

```
